An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/1.introduction.tex
small fixes

The composition of BX programs is a fundamental construct to build more complex BX programs. 
%In BX programs, composition of programs is essential for writing various interesting evaluations.
Because recursions are achieved by compositions, large number of programs include compositions.
In the BX lens papers \cite{} compositions are also known as central part of BX programs.
In this section we use a small BX program that contains compositions as a running example, because the programs including recursions can be complicated easily. The running examples are two versions of three composition of $phead$: ($phead \circ phead) \circ phead$ (we call lp3) and $phead \circ (phead \circ phead$) (we call rp3).

@@

\textcolor{red}{In this program, recursion occurs on the left-hand side of composition. Because of priority, it is impossible to tranform this program to right associative compositions. At the same time, we can not apply fusion \cite{} to this program because this program is dynamically produced depending on the length of the input list.}
Therefore it is important to have a fast evaluation method for left associative compositions.

>>>>

The composition of BX programs is a fundamental construct to build more complex BX programs. 
%In BX programs, composition of programs is essential for writing various interesting evaluations.
Because recursions are achieved by compositions, large number of programs include compositions.
In the BX lens papers \cite{} compositions are also known as central part of BX programs.
In this section we use a small BX program that contains compositions as a running example, because the programs including recursions can be complicated easily. The running examples are two versions of two composition of $phead$: ($phead \circ phead) \circ phead$ (we call lp3) and $phead \circ (phead \circ phead$) (we call rp3).

@@

\input{breverse.tex}

\noindent \textcolor{red}{In this program, recursion occurs on the left-hand side of composition. Because of priority, it is impossible to tranform this program to right associative compositions. At the same time, we can not apply fusion \cite{} to this program because this program is dynamically produced depending on the length of the input list.}
Therefore it is important to have a fast evaluation method for left associative compositions.
